Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-08-05 ms.tex
added reference info for IRAF and IDL.

\textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}. SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.}}

>>>>

\textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}. SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.\texttt{IRAF} \citep{tody86}, \texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}
